Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-03-30 fib2.tex
more minor text edits. im mostly pretty happy now with the structure. intro still needs a bunch of work, refs still need to be added, and there are a few open comments to address, especially in the conclusion.

	We consider encoding a qubit of quantum information in the global degeneracy associated with the topology of the manifold of our system. We imagine an idealized Hamiltonian for this system of the form
	\begin{align}
		H=-\sum_{i\in Lambda}\proj{\mathbb{I}_i}\;,\label{e:hamiltonian}
	\end{align}
with $\proj{\mathbb{I}}_i$ the projector to charge $\mathmm{I}$ at site $i$, i.e.~the ground space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary conditions, this space is two-fold degenerate as noted above. We identify this ground space as the codespace of our model. Typical realistic noise processes in this kind of system are pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$. It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only is sufficient to capture the qualitative features of an error-correction simulation, and so we will restrict to pair-creation noise processes in this study for convenience. These events act on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen uniformly at random at each timestep of the simulation. The simulation time, and thus the error-correction threshold, will be measured in terms of average number of noise processes per edge, as opposed to an iid noise probability per edge. The latter measure is not appropriate for error processes in nonabelian anyon models, but the two coincide in the limit of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).

@@

	Our error-correction algorithm is based on the hard-decision renormalization group (RG) decoders studied in Refs.~\cite{?}. Our decoder proceeds by measuring the occupations of anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons within each cluster, and iterating at longer length scales. It terminates when the lattice is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the total size of the lattice. \cggb{A few more details? What is our length schedule?} \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} Note that we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions RG decoders~\cite{?} \cggb{do we?}. The advantage of using a hard-decision RG decoder is its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient classical simulability of successful error-correction~\cite{RGsim}.

@@

Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent in computational power to universal quantum computing (and thus unlikely to be classically tractable), noise and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest~\cite{RGsim}. In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently 
simulate for the following heuristic reasons (see Ref.~\cite{RGsim} for a more rigorous analysis).

@@

	We plot the performance of the decoder as a function of error rate for varying lattice sizes in \Fref{f:threshold}. The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the average number of errors per edge over the simulation. We find evidence of a decoding threshold below which decoding succeeds with asymptotic certainty as the system size increases at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003$.

@@

	We have demonstrated classical simulation of successful error correction in a universal anyon model. Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to Ref.~\cite{Brell2013}. In particular, although we have modelled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. This situation would be appropriate to model error-correction routines in a topological quantum computation protocol. Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, etc.

>>>>

	We consider encoding a qubit of quantum information in the global degeneracy associated with the topology of the manifold of our system. We imagine an idealized Hamiltonian for this system of the form
	\begin{align}
		H=-\sum_{i\in \Lambda}\proj{\mathbb{I}}_i\;,\label{e:hamiltonian}
	\end{align}
with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary conditions, this space is two-fold degenerate as noted above. We identify this ground space as the codespace of our model. Typical realistic noise processes in this kind of system are pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$. It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only is sufficient to capture the qualitative features of an error-correction simulation, and so we will restrict to pair-creation noise processes in this study for convenience. These events act on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen uniformly at random at each timestep of the simulation. The simulation time, and thus the error-correction threshold, will be measured in terms of average number of noise processes per edge, as opposed to an iid noise probability per edge. The latter measure is not appropriate for error processes in nonabelian anyon models, but the two coincide in the limit of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).

@@

	Our error-correction algorithm is based on the hard-decision renormalization group (RG) decoders studied in Refs.~\cite{?}. Our decoder proceeds by measuring the occupations of anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons within each cluster, before iterating at increasing length scales. It terminates when the lattice is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the total size of the lattice. \cggb{A few more details? What is our length schedule?} \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} Note that we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions RG decoders~\cite{?} \cggb{do we?}. The advantage of using a hard-decision RG decoder is its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient classical simulability of successful error-correction~\cite{RGsim}.

@@

Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent in computational power to universal quantum computing (and thus unlikely to be classically tractable), noise processes and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest~\cite{RGsim}. In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently 
simulate for the following heuristic reasons (see Ref.~\cite{RGsim} for a more rigorous analysis).

@@

	We plot the performance of the decoder as a function of error rate for varying lattice sizes in \Fref{f:threshold}. The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the expected number of errors per edge over the simulation. We find evidence of a decoding threshold below which decoding succeeds with asymptotic certainty as the system size increases at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003$.

@@

	We have demonstrated classical simulation of successful error correction in a universal anyon model. Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. In particular, although we have modelled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. This situation would be appropriate to model error-correction routines in a topological quantum computation protocol. Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, etc.
